Initial environmental impacts of Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-08-16 manu-draft.Rmd
redtide and fish kills figure added

* Figure \@ref(fig:map) map
* Figure \@ref(fig:timeline) timeline of events
* Figure \@ref(fig:wqmap) map of water quality observations
* Figure \@ref(fig:wqtrnds) boxplots by week with +/-1sd for monthly long-term
* Figure \@ref(fig:pcacors) pca and correlations of all wq variables, by area 
* Figure \@ref(fig:trnex) seagrass and macroalgae example transect
* Figure \@ref(fig:trnfrq) seagrass, macroalgae frequency occurrence estimates
* Figure \@ref(fig:allpcacors) seagrass, macralgae, wq pca and correlation matrix
* Fig x Red tide historic and current, include fish kill reports

@@

>>>>

* Figure \@ref(fig:map) map
* Figure \@ref(fig:timeline) timeline of events
* Figure \@ref(fig:wqmap) map of water quality observations
* Figure \@ref(fig:wqtrnds) boxplots by week with +/-1sd for monthly long-term
* Figure \@ref(fig:pcacors) pca and correlations of all wq variables, by area 
* Figure \@ref(fig:trnex) seagrass and macroalgae example transect
* Figure \@ref(fig:trnfrq) seagrass, macroalgae frequency occurrence estimates
* Figure \@ref(fig:allpcacors) seagrass, macralgae, wq pca and correlation matrix
* Figure \@ref(fig:redtide) red tide historic and current, fish kill reports historic and current

@@

```{r redtide, fig.cap = '*Karenia brevis* concentrations (100k cells/L) and number of fish kill reports for the contiguous record showing cell concentrations (a) by year and (b) by week in 2021 and reported fish kills by city (Tampa, St. Petersburg) (c) by year and (d) by week in 2021. Red tide concentrations show minimum, tenth percentile, median, 90th percentile, and maximum for each year or week for middle and lower Tampa Bay. *K. brevis* cell counts are from NOAA Harmful Algal BloomS Observing System (HABSOS, https://www.ncei.noaa.gov/maps/habsos), Fish kill reports are from Florida Wildlife Research Insitute Fish Kill Database, attributed to *K. brevis* (https://public.myfwc.com/FWRI/FishKillReport/).'}
knitr::include_graphics('figs/redtide.jpeg')
```
